The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-28 paper/ms.tex
add words describing transit model fitting

\begin{figure}[!t]
    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
    \caption{
        Significance thresholds empirically defined for the transiting planet 
        search described in \S~\ref{subsec:ctois}. Each point represents the 
        TLS periodogram peak signal detection efficiency from one light curve.
        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
    }
    \label{fig:tlsresults}
\end{figure}

@@

\subsection{Objects of Interest}
\label{subsec:ctois}
The objects that all vetters identified as planet candidates were then
fit with the usual \citet{mandel_analytic_2002} model. (CITE BATMAN).
The resulting fits are shown in Figure XXX.
The parameters of the planet candidates are given in Table YYY, and
are also available as cTOIs NNN.01 - MMM.01 on exofop-TESS (LINK).

%tODO: add plots and descriptions of other nice objects too

>>>>

\begin{figure}[!t]
    \gridline{\fig{tlsresult_sector6.png}{0.45\textwidth}{}}
    \vspace{-0.8cm}
    \gridline{\fig{tlsresult_sector7.png}{0.45\textwidth}{}}
    \caption{
        Significance thresholds empirically defined for the transiting planet 
        search described in \S~\ref{subsec:identifying_ctois}. Each point represents the 
        TLS periodogram peak signal detection efficiency from one light curve.
        {\it Top.} Sector 6.  {\it Bottom.} Sector 7.
    }
    \label{fig:tlsresults}
\end{figure}

@@

\subsection{Objects of Interest}
\label{subsec:ctois}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{ctoi_quilt.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf 12 of the \numberpcs candidate transiting planets identified
    in this work.} 
    Models are fit as described in \S~\ref{subsec:ctois}.
    The full set of model parameters are in Table~XXX and on
    exofop-TESS.
	\label{fig:ctoi_quilt}
	}
\end{figure*}

If all vetters identified an object as a planet candidate, we then
proceeded to fit a transit model to the data.  The procedure closely
mirrors that used by \citet{bouma_wasp-4b_2019} to create a
phase-folded light curve for WASP-4.

First, we selected points within 5 transit durations of each transit
midpoint, using the orbital period, transit duration, and reference
epoch found from applying TLS to the detrended light curve.  We then
fitted a line to the out-of-transit flux measurements around each
transit window, and divided it out.  We then fitted a standard transit
model using the formulae given by \citet{mandel_analytic_2002} and
implemented by \citet[][\texttt{BATMAN}]{kreidberg_batman_2015}.  The
free parameters were the orbital period, the reference epoch, the
planet to star radius ratio $R_{\rm p}/R_\star$, the orbital distance
to stellar radius ratio $a/R_\star$, and the inclination $i$.  We
assumed circular orbits.  To fix the quadratic limb-darkening
parameters, we collected $T_{\rm eff}$ and $\log g$ from the TIC, and
then interpolated against the \citet{claret_limb_2017} tables.  For
stars hotter than the maximal effective temperature of these tables
($12,000\,{\rm K}$), we simply used the coefficients of the hottest
star.

We then sampled the posterior probability distribution using the
\citet{goodman_ensemble_2010} algorithm, as implemented by
\citet[][\texttt{emcee}]{foreman-mackey_emcee_2013}.  Our main goal in
this procedure was to provide an accurate ephemeris.  To ensure that
the reported uncertainties are valid, after performing the initial fit
using the photometric uncertainties reported in our light curves, we
rescaled the the uncertainty in each photometric data point to equal
the root-mean-square deviation of each transit-model subtracted light
curve. We then refitted each light curve.

The resulting parameters are given in Table YYY, and are also
available as cTOIs NNN.01 - MMM.01 on exofop-TESS (LINK).
Figure~\ref{fig:ctoi_quilt} shows the phase-folded lightcurves and
their best-fitting moels.

The physical parameters quoted in Table YYY, and on exofop-TESS,
should be considered preliminary, and could be substantially improved
with an object-by-object analysis.  A few additional assumptions were
required to report some of the values.  For the stellar radii, we
assumed the $R_\star$ values and uncertainties reported in the TIC.
There were a few cases with null uncertainties in the stellar radii --
for these, we simply invented a relative uncertainty of 30\%, and note
in the comments that this was done.  The uncertainties in e.g., the
planetary radii and impact parameters were found using linear error
propagation theory, under the idealized assumption that the covariance
between all stellar and planetary parameters was zero.

Finally, the determine the names of the objects -- that is whether
they were already TOIs, or cTOIs -- we cross-referenced based on a
combination of the TIC identifier, spatial position, and the ephemeris
of each object.
